Evaluation of classical correlation functions from 2/3D images on CPU and GPU architectures: introducing CorrelationFunctions.jl

### 2022-10-21 paper-correlations.tex
Insert plots in the paper

\subsection{Two-dimensional case}
Consider an infinite set of disks with radii $R$ and centers generated by
Poisson point process with parameter $\lambda$. \textcolor{red}{Insert picture}.

@@

\textcolor{red}{Add results}

@@

\textcolor{red}{Add results}

\begin{figure*}[t]
  \centering
  \subfigure[Lineal-path correlation function]{
    \includegraphics[width=0.475\linewidth]{images/l2-2d.png}
    \label{fig:l2-2d}}
  \hfill
  \subfigure[Two-point correlation function]{
    \includegraphics[width=0.475\linewidth]{images/s2-2d.png}
    \label{fig:s2-2d}}
  \vskip\baselineskip
  \subfigure[Surface-surface correlation function]{
    \includegraphics[width=0.475\linewidth]{images/ss-2d.png}
    \label{fig:ss-2d}}
  \hfill
  \subfigure[Surface-void correlation function]{
    \includegraphics[width=0.475\linewidth]{images/sv-2d.png}
    \label{fig:sv-2d}}
  \caption[]{A comparison of calculated values of $L_2(r)$, $S_2(r)$,
    $F_{ss}(r)$ and $F_{sv}(r)$ with theoretical values for overlapping disks.}
  \label{fig:2d}
\end{figure*}

\begin{figure*}[t]
  \centering
  \subfigure[Lineal-path correlation function]{
    \includegraphics[width=0.475\linewidth]{images/l2-3d.png}
    \label{fig:l2-3d}}
  \hfill
  \subfigure[Two-point correlation function]{
    \includegraphics[width=0.475\linewidth]{images/s2-3d.png}
    \label{fig:s3-3d}}
  \vskip\baselineskip
  \subfigure[Surface-surface correlation function]{
    \includegraphics[width=0.475\linewidth]{images/ss-3d.png}
    \label{fig:ss-3d}}
  \hfill
  \subfigure[Surface-void correlation function]{
    \includegraphics[width=0.475\linewidth]{images/sv-3d.png}
    \label{fig:sv-3d}}
  \caption[]{A comparison of calculated values of $L_2(r)$, $S_2(r)$,
    $F_{ss}(r)$ and $F_{sv}(r)$ with theoretical values for overlapping balls.}
  \label{fig:3d}
\end{figure*}

\begin{figure*}[t]
  \centering
  \subfigure[Pore size correlation function (2D)]{
    \includegraphics[width=0.475\linewidth]{images/ps-2d.png}
    \label{fig:ps-2d}}
  \hfill
  \subfigure[Chord length correlation function (2D)]{
    \includegraphics[width=0.475\linewidth]{images/cl-2d.png}
    \label{fig:cl-2d}}
  \vskip\baselineskip
  \subfigure[Pore size correlation function (3D)]{
    \includegraphics[width=0.475\linewidth]{images/ps-3d.png}
    \label{fig:ps-3d}}
  \hfill
  \subfigure[Chord length correlation function (3D)]{
    \includegraphics[width=0.475\linewidth]{images/cl-3d.png}
    \label{fig:cl-3d}}
  \caption[]{A comparison of calculated values of $P(r)$ and $p(r)$
    with theoretical values for overlapping disks (\cref{fig:ps-2d} and
    \cref{fig:cl-2d}) and balls(\cref{fig:ps-3d} and \cref{fig:cl-3d}).}
  \label{fig:pscl}
\end{figure*}

>>>>

\subsection{Two-dimensional case}
Consider an infinite set of disks with radii $R$ and centers generated by
Poisson point process with parameter $\lambda$.

@@

To test out package we generate a realization of random overlapping disks
(\cref{fig:overlapping-disks}) with dimensions $10000 \times 10000$ and
parameters $R = 40$ and $\lambda = 10^{-4}$ and compare calculated correlation
functions with their theoretical values. The results are present on
\cref{fig:verification}.
\begin{figure}[ht]
  \centering
  \includegraphics[width=0.9\linewidth]{images/disks-fragment.png}
  \caption[]{A fragment of overlapping disks used in testing of our library.}
  \label{fig:overlapping-disks}
\end{figure}

@@

To test out package we generate a realization of random overlapping disks
(\cref{fig:overlapping-disks}) with dimensions $500 \times 500 \times 500$ and
parameters $R = 10$ and $\lambda = 10^{-4}$ and compare calculated correlation
functions with their theoretical values. The results are present on
\cref{fig:verification}.

\begin{figure*}[tp]
  \centering
  \subfigure[Lineal-path correlation function]{
    \includegraphics[width=0.3\linewidth]{images/l2.png}
    \label{fig:l2}}
  \hfill
  \subfigure[Two-point correlation function]{
    \includegraphics[width=0.3\linewidth]{images/s2.png}
    \label{fig:s2}}
  \hfill
  \subfigure[Surface-surface correlation function]{
    \includegraphics[width=0.3\linewidth]{images/ss.png}
    \label{fig:ss}}
  \vskip\baselineskip
  \subfigure[Surface-void correlation function]{
    \includegraphics[width=0.3\linewidth]{images/sv.png}
    \label{fig:sv}}
  \hfill
  \subfigure[Pore size correlation function]{
    \includegraphics[width=0.3\linewidth]{images/ps.png}
    \label{fig:ps}}
  \hfill
  \subfigure[Chord length correlation function]{
    \includegraphics[width=0.3\linewidth]{images/cl.png}
    \label{fig:cl}}
  \caption[]{A comparison of calculated and theoretical values of correlation
    functions for overlapping disks and balls.}
  \label{fig:verification}
\end{figure*}
